---
title: "Good Habits in R"
subtitle: "&nbsp;"
author: "Connor Gilroy"
date: "`r Sys.Date()`"
output: 
  # html_document:
  #   css: styles.css
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, presentation-styles.css]
    lib_dir: libs
    nature:
      highlightStyle: tomorrow
      highlightLines: true
      countIncrementalSlides: false
---

class: middle, font200, clear, divide-slide

.pull-left.center.inverse[
<br/>
.font200[Principles]
]

.pull-right[

1. Use good tools

2. Write consistent code

3. Organize your work

]

---

class: center, middle, inverse, clear, font200

.font150[Use good tools]

----

---

class: font200

# Use the tidyverse

<br/>

The [tidyverse](https://www.tidyverse.org/) is

- a set of tools with consistent design
- a way of thinking about data manipulation

```{r eval=FALSE}
install.packages("tidyverse")
```




---

class: font200

# Use RMarkdown

.font90[RMarkdown lets you mix text and code in the same document:]

.pull-left.font80[

## Write in .Rmd: 

<pre>
## Header

This is some text.

```&#123;r&#125;
# r code and output
rnorm(2)
```

</pre>

]

.pull-right.font80[

## See in output: 

## Header

This is some text.

```{r}
# r code and output
rnorm(2)
```

]


---

class: center, middle, inverse, clear, font200

.font150[Write consistent code]

----

---

class: font200

# Use a standard style

<br/>

- Use spaces and indentation consistently

- Spread code out over several lines if it's too long

- Adopt a style guide, like this one: https://style.tidyverse.org/

---

class: font200

# Name things well

<br/>

*Files* and *variables* should have descriptive names

- no caps
- no spaces 
- underscores for separation

---

class: center, middle, inverse, clear, font200

.font150[Organize your work]

----

---

class: font200

# Organize your work

<br/>

- Use R projects (`.Rproj` files), and make sure you're opening data using relative paths

- Use subfolders, like a `data/` folder

- Don't save `.RData` or other extraneous stuff from your workspace. Keep it clean!

---

class: center, middle, inverse, clear, font200

.font150[Other tips]

----

---

class: font200

# Miscellaneous

- **Learn RStudio keyboard shortcuts!** For example, CMD-Enter or CTRL-Enter to run code, tab completion, up arrow for previous commands...

- **Long-term:** think about learning topics like version control, and a bit about the command line
